The abundance of Bullet-Groups in $\Lambda$CDM

### 2014-03-25 paper/ms.tex
overdensity criterion

We use DM halo catalogs constructed using the Bound Density Maxima (BDM)
algorithm \citep{BDM,BDMb}. To define the radius of a halo we use a
density threshold of 360 times the mean density of the Universe (
200 times the critical density), for different redshifts we use the
overdensity criterion by \cite{Bryan1998}. An important feature of BDM
is that it allows us to detect sub-halos inside larger virialized
structures.

@@

\ref{table:numbers}.

>>>>

We use DM halo catalogs constructed using the Bound Density Maxima (BDM)
algorithm \citep{BDM,BDMb}. To define the radius of a halo we use a
density threshold of 360 times the mean density of the Universe. An important feature of BDM is that it allows us to detect sub-halos inside larger virialized
structures.

@@
